Lab 8: Binomiaal Models in R: Answers

### 2023-03-07 Lab 8  BinomialModels/Lab8_BinomialModels.Rmd
Add files via upload

---
title: 'Lab 7: Missing Data and Imputation:Answers'
author: "Eric Parajon"
header-includes:
  - \usepackage{enumerate}
  - \usepackage{graphicx}
output: pdf_document
---

@@

rm(list=ls()) # clear workspace
#setwd("____") # change to wherever you saved the data
set.seed(18765) # set seed for replication

@@

Today, we're going to simulate predicted probabilities for a model with an interaction term and plot our results. We will use both the average case and the observed-case approaches.

@@

+ Average-Case Approach: Simulate and plot predicted probabilities over the range of age, holding all other variables at their mean, for the second model. Plot this.

+ Observed-Case Approach: Generate an average predicted effect over the observed values of income for the first model. Plot this too.

@@

sim_betas <- mvrnorm(______)

@@

sim_gg <- data.frame(age = ______, pe = apply(sim_pp, 1, mean),
                     lo = ______,
                     hi = ______)

ggplot()

@@

#getting sim betas for m1
sim_betas_m1 <- mvrnorm(______)

#getting range of income
income_vec <- seq(from = ______,
                  length.out = 100)

@@

ggplot(______)

>>>>

---
title: 'Lab 8: Binomiaal Models in R'
author: "Eric Parajon"
header-includes:
- \usepackage{enumerate}
- \usepackage{graphicx}
output:
  html_document:
    df_print: paged
---

@@

rm(list=ls()) # clear workspace
#setwd("____") # change to wherever you saved the data
set.seed(1234) # set seed for replication

@@

Today, we're going to simulate predicted probabilities for a model with an interaction term, use the distribution of these simulated probabilities to define confidence intervals, and plot our results, using both the average case and the observed-case approaches.

@@

+ Average-Case Approach: Simulate and plot predicted probabilities over the range of **age**, holding all other variables at their mean, for the second model. Plot this.

+ Observed-Case Approach: Generate an average predicted effect over the observed values of **income** for the first model. Plot this too.

@@

sim_betas <- mvrnorm(______,______, vcov(m2))

@@

sim_gg <- data.frame(age = ______, pe = apply(sim_pp, 1, mean),
                     lo = apply(sim_pp, 1, quantile, probs = .025),
                     hi = ______)

ggplot(sim_gg, aes(x = age, y = pe, ymin = lo, ymax = hi)) +
        ______

@@

#getting sim betas for m1
sim_betas_m1 <- mvrnorm(______,______,vcov(m1))

#getting range of income
income_vec <- seq(from = min(turnout$income),to=____),
                  length.out = 100)

@@

ggplot(plotdat, aes(x = income, y = pe, ymin = lo, ymax = hi)) +
          ______

### 2023-03-07 Lab 8  BinomialModels/Lab8_BinomialModels_AnswerKey.Rmd
Add files via upload

---
title: 'Lab 8: Binomiaal Models in R'
author: "TA: Eric Parajon"
output: pdf_document
---

@@

We talked about simulations in Lab 4, when we talked about OLS. This time around, we will do similar things, but with non-Normal outcomes, where simulations are even more helpful!

>>>>

---
title: 'Lab 8: Binomiaal Models in R: Answers'
author: 'TA: Eric Parajon'
output:
  html_document:
    df_print: paged
---

@@

Simulation strikes again! This time around, we will do similar things, but with non-Normal outcomes, where simulations are even more helpful.
